---
title: "Final Project"
author: "Eghosa Ogbeide"
format: 
  html:
    theme: quartz
execute:
  echo: false
---

## Superbowl Ads

This table is a summary of ads from the 10 brands that had the most advertisements in Super Bowls from 2000 to 2020, according to data from [superbowl-ads.com](https://www.superbowl-ads.com), with matching videos found on YouTube. FiveThirtyEight staffers then came up with seven defining characteristics of a Super Bowl ad, watched every video and evaluated each according to the taxonomy in the table below.
```{r}
#| message: false
library(tidyverse)
library(gtsummary)
library(dplyr)
#Load data
superbowl_ads <- read_csv(here::here("data", "superbowl-ads.csv")) |>
	mutate(across(
		c(funny, show_product_quickly, patriotic, celebrity, danger, animals,use_sex),
		~ factor(., levels = c(FALSE, TRUE), labels = c("No", "Yes"))
	))

```

```{r}
#| label: tbl-brand
#| tbl-cap: "Descriptive statistics characterizing 10 Brands' Superbowl Ads"

#Create a GTsummary of Superbowl Ads data by Brands
tbl_brand <- tbl_summary(
	superbowl_ads,
	by = brand,
	include = c(
		funny, show_product_quickly,
		patriotic, celebrity, danger, animals
	),
	label = list(
		funny ~ "Funny Ads",
		show_product_quickly ~ "Ads showed the product right away",
		patriotic ~ "Patriotic Ads",
		celebrity ~ "Celebrity-featured Ads",
		danger ~ "Ads involving danger",
		animals ~ "Animals-featured Ads"
	),
	missing_text = "Missing"
)|>
add_overall(col_label = "**Total** N = {N}") |>
	bold_labels()
tbl_brand
```

```{r}
logistic_model <- glm(funny ~ show_product_quickly + patriotic + celebrity + danger,
											data = superbowl_ads, family = binomial()
)

tbl_regression(
	logistic_model,
	exponentiate = TRUE,
	label = list(
		show_product_quickly ~ "Did it show the product right away?",
		patriotic ~ "Was it Patriotic",
		celebrity ~ "Did it feature a celebrity? ",
		danger ~ "Did it involve danger?"
	),
	missing_text = "Missing"
)|>
	bold_labels() |>
	modify_caption("**Funny Superbowl Ads Multivariable Regression Fit**")

```

