---
title: "Final Project"
author: "Eghosa Ogbeide"
format: 
  html:
    theme: quartz
execute:
  echo: false
---

## Superbowl Ads

This table is a summary of ads from the 10 brands that had the most advertisements in Super Bowls from 2000 to 2020, according to data from [superbowl-ads.com](https://www.superbowl-ads.com), with matching videos found on YouTube. FiveThirtyEight staffers then came up with seven defining characteristics of a Super Bowl ad, watched every video and evaluated each according to the taxonomy in the table below.

```{r}
#| message: false
library(dplyr)
library(tidyverse)
library(gtsummary)
library(janitor)
library(broom)
library(ggplot2)
library(tidycat)
#Load data
superbowl_ads <- read_csv(here::here("data", "superbowl-ads.csv")) |>
	mutate(across(
		c(funny, show_product_quickly, patriotic, celebrity, danger, animals,use_sex),
		~ factor(., levels = c(FALSE, TRUE), labels = c("No", "Yes"))
	))

```

```{r}
#| label: tbl-brand
#| tbl-cap: "Descriptive statistics characterizing 10 Brands' Superbowl Ads"

#Create a GTsummary of Superbowl Ads data by Brands
tbl_brand <- tbl_summary(
	superbowl_ads,
	by = brand,
	include = c(
		funny, show_product_quickly,
		patriotic, celebrity, danger, animals,use_sex
	),
	label = list(
		funny ~ "Funny Ads",
		show_product_quickly ~ "Ads showed the product right away",
		patriotic ~ "Patriotic Ads",
		celebrity ~ "Celebrity-featured Ads",
		danger ~ "Ads involving danger",
		animals ~ "Animals-featured Ads",
		use_sex~ "Ads that use sex appeal"
	),
	missing_text = "Missing"
)|>
add_overall(col_label = "**Total** N = {N}") |>
	bold_labels()
tbl_brand
```

The percentage of Budweiser ads that were patriotic and included animals is `r round(mean(superbowl_ads$animals[superbowl_ads$brand == "Budweiser"] == "Yes" & superbowl_ads$patriotic[superbowl_ads$brand == "Budweiser"] == "Yes", na.rm = TRUE) * 100, 1)`%.

```{r}
pct_dataset_by_brand <-round(mean(superbowl_ads$brand == "Hyundai" & superbowl_ads$funny == "Yes" & superbowl_ads$patriotic == "Yes", na.rm = TRUE) * 100, 1)
```

The percentage of Hyundai ads that were both funny and patriotic among all the Super Bowl ads is `r pct_dataset_by_brand`%.

```{r}
inline_text(tbl_brand,variable = "patriotic",
            column = "Budweiser")
```

In @tbl-brand above, `r inline_text(tbl_brand,variable = "patriotic",column = "stat_5")` of E-Trade ads were patriotic.

```{r}
funny_dori <- inline_text(tbl_brand, variable = funny, column = "Doritos")
funny_cola <- inline_text(tbl_brand, variable = funny, column = "Coca-Cola")
```

Additionally, a greater proportion of Doritos ads (`r funny_dori`) than Coca-Cola (`r funny_cola`) ads were funny.

*In @tbl-funnyreg, is a multivariable regression fit to determine if there is an association between funny Super Bowl ads and other characteristics, to examine and assess the relationship between Superbowl ads characteristics. The results are shown below.*

```{r}
#| label: tbl-funnyreg
#| tbl-cap: "Funny Superbowl Ads Multivariable Regression Fit"

#Create a GTsummary of Superbowl Ads data by Brands

logistic_model <- glm(funny ~ show_product_quickly + patriotic + celebrity + danger,
											data = superbowl_ads, family = binomial()
)

tbl_funnyreg <- tbl_regression(
	logistic_model,
	exponentiate = TRUE,
	label = list(
		show_product_quickly ~ "Did it show the product right away?",
		patriotic ~ "Was it Patriotic",
		celebrity ~ "Did it feature a celebrity? ",
		danger ~ "Did it involve danger?"
	),
	missing_text = "Missing"
)|>
	bold_labels()
tbl_funnyreg
tidy_fun = broom.helpers::tidy_parameters
```

As shown in @tbl-funnyreg, the odds of a funny superbowl ad involving danger is 4.23 times the odds of a funny superbowl ad not involving danger.

*The figure below displays the frequency of ads by Brand Advertisers from 2000 to 2020.*
```{r}
#| label: fig-brand-freq
#| fig-cap: "Frequency of Super Bowl Ads by Brand"
brand_figure<- ggplot(data = {superbowl_ads},
			 aes(x = {brand}, fill = brand),) +
	geom_bar() + labs(title = "Frequency of Ads by Brand Advertisers from 2000 to 2020")
brand_figure
```

As seen in @fig-brand-freq, Bud Light had the greatest number of Super Bowl ads between 2000 and 2020.


@tbl-topbrand provides Super Bowl ad characteristics by brand in 2015.
```{r}
#| label: tbl-topbrand
#| tbl-cap: "Ad characteristics by Brand, 2015"

tbl_top_brands <- superbowl_ads |> filter(year == 2015) |>
	tbl_summary(
	by = brand,
	include = c(
		funny, show_product_quickly,
		patriotic, celebrity, danger, animals
	),
	label = list(
		funny ~ "Funny Ads",
		show_product_quickly ~ "Ads showed the product right away",
		patriotic ~ "Patriotic Ads",
		celebrity ~ "Celebrity-featured Ads",
		danger ~ "Ads involving danger",
		animals ~ "Animals-featured Ads"
	),
	missing_text = "Missing"
)|> 
add_overall(col_label = "**Total** N = {N}") |>
	bold_labels()
tbl_top_brands
```
