---
title: "Final Project"
author: "Eghosa Ogbeide"
format: 
  html:
    theme: quartz
execute:
  echo: false
---

## Superbowl Ads

This table is a summary of ads from the 10 brands that had the most advertisements in Super Bowls from 2000 to 2020, according to data from [superbowl-ads.com](https://www.superbowl-ads.com), with matching videos found on YouTube. FiveThirtyEight staffers then came up with seven defining characteristics of a Super Bowl ad, watched every video and evaluated each according to the taxonomy in the table below.
```{r}
#| message: false
library(dplyr)
library(tidyverse)
library(gtsummary)
library(janitor)
library(broom)
library(ggplot2)
library(tidycat)
#Load data
superbowl_ads <- read_csv(here::here("data", "superbowl-ads.csv")) |>
	mutate(across(
		c(funny, show_product_quickly, patriotic, celebrity, danger, animals,use_sex),
		~ factor(., levels = c(FALSE, TRUE), labels = c("No", "Yes"))
	))

```

```{r}
#| label: tbl-brand
#| tbl-cap: "Descriptive statistics characterizing 10 Brands' Superbowl Ads"

#Create a GTsummary of Superbowl Ads data by Brands
tbl_brand <- tbl_summary(
	superbowl_ads,
	by = brand,
	include = c(
		funny, show_product_quickly,
		patriotic, celebrity, danger, animals
	),
	label = list(
		funny ~ "Funny Ads",
		show_product_quickly ~ "Ads showed the product right away",
		patriotic ~ "Patriotic Ads",
		celebrity ~ "Celebrity-featured Ads",
		danger ~ "Ads involving danger",
		animals ~ "Animals-featured Ads"
	),
	missing_text = "Missing"
)|>
add_overall(col_label = "**Total** N = {N}") |>
	bold_labels()
tbl_brand
```

```{r}
inline_text(tbl_brand,variable = "patriotic",
            column = "Budweiser")
```
In the sample above, `r inline_text(tbl_brand,variable = "patriotic",column = "Budweiser")` of Budweiser ads were patriotic.'

```{r}
funny_dori <- inline_text(tbl_brand, variable = funny, column = "Doritos")
funny_cola <- inline_text(tbl_brand, variable = funny, column = "Coca-Cola")
```

Additionally, a greater proportion of Doritos ads (`r funny_dori`) than Coca-Cola (`r funny_cola`) ads were funny.


```{r}
#| label: tbl-regression
#| tbl-cap: "Funny Superbowl Ads Multivariable Regression Fit"

#Create a GTsummary of Superbowl Ads data by Brands

logistic_model <- glm(funny ~ show_product_quickly + patriotic + celebrity + danger,
											data = superbowl_ads, family = binomial()
)

tbl_funnyreg <- tbl_regression(
	logistic_model,
	exponentiate = TRUE,
	label = list(
		show_product_quickly ~ "Did it show the product right away?",
		patriotic ~ "Was it Patriotic",
		celebrity ~ "Did it feature a celebrity? ",
		danger ~ "Did it involve danger?"
	),
	missing_text = "Missing"
)|>
	bold_labels()
tbl_funnyreg
tidy_fun = broom.helpers::tidy_parameters
```

```{r}
brand_figure<- ggplot(data = {superbowl_ads},
			 aes(x = {brand}, fill = brand),) +
	geom_bar() + labs(title = "Frequency of Ads by Brand Advertisers")
brand_figure
```


```{r}
#| label: tbl-topbrand
#| tbl-cap: "Table of Top Brands"

tbl_top_brands <- tbl_summary(
	superbowl_ads,
	by = year,
	include = c(
		brand,
	),
	label = list(
		brand ~ "Brands"
	),
	missing_text = "Missing"
)|>
add_overall(col_label = "**Total** N = {N}") |>
	bold_labels()
tbl_top_brands
```


